### 2021-04-09 input/figproblem.tex
still on examples mostly

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figproblemA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:problemB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figproblemB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:problemC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figproblemC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:problemD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Partition removals cannot rely only on
    current partition, for it may lead to either inconsistent
    partitioning, or every process receiving every broadcast.}
\end{figure*}

>>>>

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both Process~$a$ and
      Process~$d$ add then delete their partition. For the recall,
      $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
      3$.]{\input{input/figproblemA.tex}}
    \hspace{5pt} \subfloat[Part B][\label{fig:problemB}Process~$b$
      delivers and forwards the $\alpha$ message about $P_a$ while
      Process~$c$ delivers and forwards both $\alpha$ and $\delta$
      messages about $P_d$.]  {\input{input/figproblemB.tex}}
    \hspace{5pt} \subfloat[Part C][\label{fig:problemC}Process~$b$
      already blocks the propagation of $\delta_a$ despite it
      propagated $\alpha_a$ before. Process~$c$ and Process~$d$ do not
      deliver $\alpha_d$, for they already deleted
      it before.]{\input{input/figproblemC.tex}}
    \hspace{5pt} \subfloat[Part D][\label{fig:problemD}Processes
      discard remaining messages. Since Process~$b$ cannot deliver
      $\delta_a$, $c$ and $d$ remain in the deleted partition
      $P_a$.]{\input{input/figproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Naive propagation of $\alpha$ and
    $\delta$ messages is insufficient to guarantee consistent partitioning.}
\end{figure*}

### 2021-04-09 input/proposal.tex
still on examples mostly

Unfortunately, stale control information about deleted partitions may
impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about other deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} highlights such consistency issue with
dynamic partitions. Both Process~$a$ and Process~$d$ add then delete
their partition concurrently. Assuming \TODO{FIFO communication
  links}, Process~$c$ receives, delivers, and forwards $\alpha_d^3$
followed by $\delta_d$. In the meantime, Process~$b$ receives,
delivers, and forwards $\alpha_a^2$. In Figure~\ref{fig:problemC},
both Process~$c$ and Process~$d$ deliver the message about Partition
$P_a$, for they did not have any known partition at receipt time. On
the contrary, Process~$b$ delivers $\alpha_d^1$, for it improves its
distance to a known source. Process~$b$ then blocks Process~$a$'s
removal notification $\delta_a$. It never reaches Process~$c$ nor
Process~$d$. Also, Process~$c$ and Process~$d$ do not deliver any
$\alpha_d$ or $\delta_d$ since they already delivered it. The system
converges to an unconsistent state where some processes assume they
belong to a partition while it does not exist any longer.

Dynamic consistent partitioning depends on receipt orders at each
processes. \TODO{Transition.}

>>>>

Unfortunately, stale control information about deleted partitions may
impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about other deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} highlights such consistency issue with
dynamic partitions, even in contexts where processes have FIFO links,
\ie where processes receive the messages in the order of their
sending. Both Process~$a$ and Process~$d$ add then delete their
partition concurrently. Process~$c$ receives, delivers, and forwards
$\alpha_d^3$ followed by $\delta_d$. In the meantime, Process~$b$
receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, both Process~$c$ and Process~$d$ deliver
the message about Partition $P_a$, for they did not have any known
partition at receipt time. On the contrary, Process~$b$ delivers
$\alpha_d^1$, for it improves its distance to a known
source. Process~$b$ then blocks Process~$a$'s removal notification
$\delta_a$. It never reaches Process~$c$ nor Process~$d$. Also,
Process~$c$ and Process~$d$ do not deliver any $\alpha_d$ or
$\delta_d$ since they already delivered it. The system converges to an
unconsistent state where some processes assume they belong to a
partition while it does not exist anymore. Naive propagation of
$\alpha$ and $\delta$ messages is insufficient to guarantee consistent
partitioning when each process can add or delete its partition at any
time.

To identify and solve the issue with dynamic consistent partitioning
where protocols enable processes to \texttt{Add} and \texttt{Del} at
any time, we need to further constrain the delivery order at each
process.
